The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl

### 2018-01-24 master.tex
jan 24 (small correction in the master file)

\author{Ch. Nicolas}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Wandared Pokapanich}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Th. Saisopa}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{P. Songsiriritthigul}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

\author{Y. Rattanachai}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

@@

\author{Ralph P\"{u}ttner}
\affiliation{Sorbonne Universit\'{e}s, UPMC Univ Paris 06, UMR 7614, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, F-75005 Paris, France}

>>>>

\author{Ralph P\"{u}ttner}
\affiliation{Fachbereich Physik, Freie Universit\"at Berlin, Arnimallee 14, D-14195, Berlin, Germany}

\author{Ch. Nicolas}
\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}

\author{Wandared Pokapanich}
\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000 Thailand}

\author{Th. Saisopa}
\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}

\author{P. Songsiriritthigul}
\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}

\author{Y. Rattanachai}
\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}

@@
